Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-20 analysis/paper/paper.Rmd
Remove a comment or two in the Rmd

```{r fonts, include=FALSE, message=FALSE, eval=FALSE}
# Note 1: This chunk only needs to be run once on a computer to import fonts for
# use in R. This chunk makes .ttf fonts available to R for use and embedding in
# .eps figure outputs.
#
# Note 2: GhostScript needs to be installed at the system level for the PS files
# to be generated.  MacOS users can use `brew install ghostscript`.  Windows
# users should download and install. Linux users can use their package manager.
#
# Note 3: You may need to tell R where to find GhostScript's 'gs' executable.
# Set `R_GSCMD="/opt/homebrew/bin/gs"` in .Renviron for MacOS users using
# homebrew to install on a Mac M1.
# 
# Windows users can follow these directions:
# 1.	Go to the GhostScript website
#  (https://www.ghostscript.com/download/gsdnld.html)
# 2.	Download the windows installer suitable for your machine
# 3.	Run the installer file which you downloaded and follow the prompts
# 4.	After running the installer click the windows "Start" button and type
# "Edit environment variables for your account" and open
# 5.	In the tab 'Advanced' click the button at the bottom
# 'Environment Variables...'
# 6.	Under 'System variables' find the variable 'Path', select 'Path' and click
# the 'Edit' button
# 7. 	Select a new line and copy the Ghostscript 'bin' folder location into the
# field.
## 7.1	If you installed ghostscript to the default folder location; then the
# folder location will likely be "C:\Program Files\gs\gs9.52\bin", the version
# number (9.52) may differ.
# 8.	Save and exit the environmental variables window
# This chunk is then run only if knitting on new computer that the files have
# not been generated

@@

<!--# not sure we need a separate section for definitions, but present continuously in the text -->

>>>>

```{r fonts, include=FALSE, message=FALSE, eval=FALSE}
# Note 1: This chunk only needs to be run once on a computer to import fonts for
# use in R. This chunk makes .ttf fonts available to R for use and embedding in
# .eps figure outputs.
#
# Note 2: GhostScript needs to be installed at the system level for the PS files
# to be generated.  MacOS users can use `brew install ghostscript`.  Windows
# users should download and install. Linux users can use their package manager.
#
# Note 3: You may need to tell R where to find GhostScript's 'gs' executable.
# Set `R_GSCMD="/opt/homebrew/bin/gs"` in .Renviron for MacOS users using
# homebrew to install on a Mac M1.
# 
# Windows users can follow these directions:
# 1.	Go to the GhostScript website
#     <https://www.ghostscript.com/download/gsdnld.html>.
# 2.	Download the windows installer suitable for your machine
# 3.	Run the installer file which you downloaded and follow the prompts
# 4.	After running the installer click the windows "Start" button and type
#     "Edit environment variables for your account" and open
# 5.	In the tab 'Advanced' click the button at the bottom
#     'Environment Variables...'
# 6.	Under 'System variables' find the variable 'Path', select 'Path' and click
#     the 'Edit' button
# 7. 	Select a new line and copy the Ghostscript 'bin' folder location into the
#     field.
## 7.1	If you installed Ghostscript to the default folder location; then the
#     folder location will likely be "C:\Program Files\gs\gs9.52\bin", the
#     version number (9.52) may differ.
# 8.	Save and exit the environmental variables window
#
# This chunk is then run only if knitting on new computer that the files have
# not been generated

@@
